---
title: "EM2_Data_Analysis"
output: html_document
date: "2025-12-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# EM2 Data Analysis

## Packages and working directory

```{r}
library(readr)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggplot2)
library(viridis)  # for colorblind-friendly palette
library(afex)
library(emmeans)
library(brms)
library(rstan)
library(zoo)
library(performance)
library(partR2)
library(effectsize)

```

```{r}
setwd("C:/Users/Safir/OneDrive/KU/03Semester/EM_2/EM2_Experiment_pschyopy")
```

## Cleaning data

Cleaning functions (removing backwards motion, replacing unsuccessful trials with NaN, clean participant trials)

```{r}
#Removing any backwards motion:
clean_after_max <- function(df) {
  df %>%
    arrange(trial, time) %>%
    group_by(trial) %>%
    group_modify(~ {
      if (!"x" %in% colnames(.x) || all(is.na(.x$x))) {
        return(.x) # return as is if x missing or all NA
      } else {
        slice_head(.x, n = which.max(.x$x))
      }
    }) %>%
    ungroup()
}

# Replace trajectory data with NaN for unsuccessful trials
mark_unsuccessful_trials <- function(df, unsuccessful_trials) {
  df %>%
    mutate(
      x = if_else(trial %in% unsuccessful_trials, NaN, x),
      y = if_else(trial %in% unsuccessful_trials, NaN, y),
      distance = if_else(trial %in% unsuccessful_trials, NaN, distance)
    )
}

# Clean a single participant's data
clean_participant <- function(df, unsuccessful_trials_training = c(), unsuccessful_trials_test = c()) {
  
  training_df <- df %>%
    filter(phase == "training") %>%
    clean_after_max() %>%
    mark_unsuccessful_trials(unsuccessful_trials_training)
  
  test_df <- df %>%
    filter(phase == "test") %>%
    clean_after_max() %>%
    mark_unsuccessful_trials(unsuccessful_trials_test)
  
  bind_rows(training_df, test_df)
}
```

Unsucessfull trials

```{r}
# Example: list of unsuccessful trials per participant
unsuccessful_trials_list <- list(
  p001 = list(training = c(1), test = c()),
  p002 = list(training = c(2), test = c()),
  p004 = list(training = c(), test = c()),
  p005 = list(training = c(), test = c(2, 3)),
  p006 = list(training = c(), test = c()),
  p007 = list(training = c(), test = c(12)),
  p008 = list(training = c(), test = c()),
  p009 = list(training = c(), test = c()),
  p010 = list(training = c(), test = c(7, 8, 14)),
  p012 = list(training = c(1), test = c()),
  p013 = list(training = c(), test = c()),
  p014 = list(training = c(12), test = c()),
  p015 = list(training = c(), test = c()),
  p017 = list(training = c(4,24), test = c()),
  p018 = list(training = c(1,2,21), test = c()),
  p019 = list(training = c(1,2,3,4,5), test = c()),
  p020 = list(training = c(1, 2, 3, 4), test = c()),
  p021 = list(training = c(), test = c()),
  p022 = list(training = c(), test = c()),
  p024 = list(training = c(), test = c()),
  p025 = list(training = c(1), test = c())
)
```

Adding self-report modal reliance

```{r}
participant_reliance <- c(
  p001 = "P",
  p002 = "P",
  p004 = "A",
  p005 = "A",
  p006 = "A, P",
  p007 = "A",
  p008 = "A",
  p009 = "A",
  p010 = "A",
  p012 = "A",
  p013 = "A",
  p014 = "P",
  p015 = "A, P",
  p017 = "A",
  p018 = "A",
  p019 = "P",
  p020 = "P",
  p021 = "A",
  p022 = "A",
  p024 = "A",
  p025 = "P"
)
```

Test group/block specification

```{r}
# Participant block assignment
participant_blocks <- c(
  p001 = 1, p009 = 1, p010 = 1, p012 = 1, p014 = 1, p018 = 1, p020 = 1, p021 = 1, p024 = 1, p025 = 1,
  p002 = 2, p004 = 2, p007 = 2, p015 = 2, p019 = 2, p022 = 2,
  p005 = 3, p006 = 3, p008 = 3, p013 = 3, p017 = 3
)
```

### Load and clean data

```{r}
# Specify folder and unsuccessful trials
data_folder <- "data/data_backup"

# Get list of CSV files
csv_files <- list.files(data_folder, pattern = "\\.csv$", full.names = TRUE)

alldata <-  map_dfr(csv_files, function(file) {
  # Extract participant ID from filename
  participant_num <- str_extract(basename(file), "\\d+")
  participant_id <- paste0("p", str_pad(participant_num, 3, pad = "0"))
  
  df <- read_csv(file)
  
  df <- df %>% rename_with(~tolower(.x))
    
  df <- df %>% mutate(distance = sqrt((x - 350)^2 + y^2))

  # Filter for participant's block
  block_num <- participant_blocks[participant_id]
  df <- df %>% filter(block == block_num)
  
  unsuccessful_trials_training <-   unsuccessful_trials_list[[participant_id]]$training
  unsuccessful_trials_test <- unsuccessful_trials_list[[participant_id]]$test
  
  # Clean participant's data
  df <- clean_participant(df, unsuccessful_trials_training, unsuccessful_trials_test)
  
  df <- df %>%
    mutate(reliance = participant_reliance[participant_id])
  
  
  df

})
```

Save as a CSV file

```{r}
write_csv(alldata, "alldata_cleaned.csv")
```

## Adding stuff

Load cleaned data

```{r}
#loading data from the cleaned data file
alldataloaded <- read_csv("alldata_cleaned.csv", show_col_types = FALSE)
```

```{r}
#distance to goal
alldataloaded <- alldataloaded %>%
  group_by(trial) %>%
  mutate(
    # Find distance at maximum x in the trial
    distance_at_max_x = distance[which.max(x)]
  )
```

## Data frames

```{r}
#separate for each block/group
alldataloaded_block_1 <- alldataloaded %>%
  filter(block == 1)

alldataloaded_block_2 <- alldataloaded %>%
  filter(block == 2)

alldataloaded_block_3 <- alldataloaded %>%
  filter(block == 3)

### 10 last and 10 first trials ###
# Define number of trials to select
n_training <- 10
n_test <- 10

#Block 1
train_test_b1 <- alldataloaded_block_1 %>%
  group_by(id, reliance, phase) %>%
  # keep last 10 training and first 10 test trials
  filter(
    (phase == "training" & trial > max(trial) - n_training) |
    (phase == "test" & trial <= n_test)
  ) %>%
  group_by(id, reliance, phase, trial) %>%
  slice_tail(n = 1) %>%     # last row per trial
  ungroup()

#set level
train_test_b1$phase <- factor(train_test_b1$phase, 
                              levels = c("training", "test"))

#Block 2
train_test_b2 <- alldataloaded_block_2 %>%
  group_by(id, reliance, phase) %>%
  # keep last 10 training and first 10 test trials
  filter(
    (phase == "training" & trial > max(trial) - n_training) |
    (phase == "test" & trial <= n_test)
  ) %>%
  group_by(id, reliance, phase, trial) %>%
  slice_tail(n = 1) %>%     # last row per trial
  ungroup()

#set level
train_test_b2$phase <- factor(train_test_b2$phase, 
                              levels = c("training", "test"))

#Block 3
train_test_b3 <- alldataloaded_block_3 %>%
  group_by(id, reliance, phase) %>%
  # keep last 10 training and first 10 test trials
  filter(
    (phase == "training" & trial > max(trial) - n_training) |
    (phase == "test" & trial <= n_test)
  ) %>%
  group_by(id, reliance, phase, trial) %>%
  slice_tail(n = 1) %>%     # last row per trial
  ungroup()

#set level
train_test_b3$phase <- factor(train_test_b3$phase, 
                              levels = c("training", "test"))
```

Blocks 1 and 2

```{r}
#Make a dataframe with both
train_b12_test_b12 <- rbind(alldataloaded_block_1, alldataloaded_block_2)

#filter for last 10 and first 10
train_test_b12 <- train_b12_test_b12 %>%
  group_by(id, reliance, phase, block) %>%
  # keep last 10 training and first 10 test trials
  filter(
    (phase == "training" & trial > max(trial) - n_training) |
    (phase == "test" & trial <= n_test)
  ) %>%
  group_by(id, reliance, phase, trial, block) %>%
  slice_tail(n = 1) %>%     # last row per trial
  ungroup()

train_test_b12$phase <- factor(train_test_b12$phase, 
                              levels = c("training", "test"))
```

Blocks 1 and 3

```{r}
train_test_b13 <- bind_rows(train_test_b1, train_test_b3)
```

For smoothed plot:

```{r}
train_b12_test_b12$phase <- factor(train_b12_test_b12$phase, levels = c("training", "test"))

last_train_b12_test_b12 <- train_b12_test_b12 %>%
  group_by(id, reliance, phase, trial, block) %>%
  slice_tail(n = 1) %>%     # last row per trial
  ungroup()

### ---- SUMMARY STATS (mean & SD per phase × trial) ---- ###
summary_df_allb12 <- last_train_b12_test_b12 %>%
  group_by(phase, trial) %>%    # phases: training/test
  summarise(
    mean_dist = mean(distance, na.rm = TRUE),
    sd_dist   = sd(distance, na.rm = TRUE),
    n         = sum(!is.na(distance)),
    .groups = "drop"
  )

max_training <- summary_df_allb12 %>%
  filter(phase == "training") %>%
  summarise(max_trial = max(trial)) %>%
  pull(max_trial)

summary_df_allb12 <- summary_df_allb12 %>%
  mutate(global_trial = ifelse(phase == "training",
                               trial,
                               trial + max_training))

summary_df_allb12 <- summary_df_allb12 %>%
  mutate(
    mean_dist_mm = mean_dist / 2.108,
    sd_dist_mm   = sd_dist   / 2.108
  )

summary_smoothed <- summary_df_allb12 %>%
  group_by(phase) %>%
  arrange(global_trial) %>%
  mutate(
    mean_dist_smooth = rollapply(mean_dist_mm, width = 3, mean, fill = NA),
    sd_dist_smooth   = rollapply(sd_dist_mm,   width = 3, mean, fill = NA)
    )


######
summary_stats_block_12$phase <- factor(
  summary_stats_block_12$phase,
  levels = c("training", "test")
)
summary_stats_block_12 <- summary_stats_block_12 %>%
  mutate(
    mean_dist_mm = mean_distance / 2.108,
    sd_dist_mm   = sd_distance   / 2.108
  )




overall_summary <- summary_stats_block_12 %>%
  group_by(phase) %>%
  summarise(
    overall_mean_mm = mean(mean_dist_mm, na.rm = TRUE),
    overall_sd_mm   = sd(mean_dist_mm, na.rm = TRUE),
    .groups = "drop"
  )

```

For speed calculations

```{r}
speed_ind <- alldataloaded %>%
  
  # Keep last 10 training and first 10 test trials PER participant
  group_by(id, phase) %>%
  filter(
    (phase == "training" & trial >= max(trial) - (n_training - 1)) |
    (phase == "test" & trial <= n_test)
  ) %>%
  
  # Now work per participant × phase × trial
  group_by(id, phase, trial) %>%
  
  summarise(
    # First and last positions
    x_start = first(x),
    y_start = first(y),
    x_end   = last(x),
    y_end   = last(y),
    
    # First and last times
    t_start = first(time),
    t_end   = last(time),
    
    # Distance to goal (keep column)
    distance_goal = last(distance)/2.108,
    
    block = first(block),
    
    .groups = "drop"
  ) %>%
  
  mutate(
    # Distance in pixels
    dist_px = sqrt((x_end - x_start)^2 + (y_end - y_start)^2),
    
    # Convert to mm
    dist_mm = dist_px / 2.108,
    
    # Time difference (seconds)
    time_s  = t_end - t_start,
    
    # Speed (mm/s)
    speed_mm_s = dist_mm / time_s
  )


speed_ind
```

```{r}
last_5cm_px <- 50 * 2.108

speed_last5cm_path <- alldataloaded %>%
  
  filter(block %in% c(1, 2)) %>%
  
  group_by(id, phase) %>%
  filter(
    (phase == "training" & trial >= max(trial) - (n_training - 1)) |
    (phase == "test" & trial <= n_test)
  ) %>%
  
  group_by(id, phase, trial, block) %>%
  arrange(time, .by_group = TRUE) %>%
  
  # last 5 cm only
  filter(distance <= last_5cm_px) %>%
  
  mutate(
    dx = x - lag(x),
    dy = y - lag(y),
    dt = time - lag(time),
    
    step_px = sqrt(dx^2 + dy^2),
    step_mm = step_px / 2.108,
    
    speed_mm_s = step_mm / dt
  ) %>%
  
  filter(!is.na(speed_mm_s), dt > 0) %>%
  
  mutate(
    path_mm = cumsum(step_mm)
  ) %>%
  
  ungroup()

```

```{r}

```

## Descriptive stats for each participant

Block 1

```{r}
#Block 1
summary_stats_block_1 <- alldataloaded_block_1 %>%
  group_by(id, phase) %>%
  # Filter for the last 10 training trials and first 10 test trials
  filter(
    (phase == "training" & trial > max(trial) - n_training) |
    (phase == "test" & trial <= n_test)
  ) %>%
  group_by(id, phase, trial) %>%
  # Keep only the last row of each trial
  slice_tail(n = 1) %>%
  ungroup() %>%
  group_by(id, phase) %>%
  summarise(
    mean_distance = mean(distance, na.rm = TRUE),
    sd_distance = sd(distance, na.rm = TRUE),
    .groups = "drop"
  )

summary_stats_block_1
```

Block 2

```{r}
#Block 2
summary_stats_block_2 <- alldataloaded_block_2 %>%
  group_by(id, phase) %>%
  # Filter for the last 10 training trials and first 10 test trials
  filter(
    (phase == "training" & trial > max(trial) - n_training) |
    (phase == "test" & trial <= n_test)
  ) %>%
  group_by(id, phase, trial) %>%
  # Keep only the last row of each trial
  slice_tail(n = 1) %>%
  ungroup() %>%
  group_by(id, phase) %>%
  summarise(
    mean_distance = mean(distance, na.rm = TRUE),
    sd_distance = sd(distance, na.rm = TRUE),
    .groups = "drop"
  )

summary_stats_block_2
```

Block 3

```{r}
#block 3
summary_stats_block_3 <- alldataloaded_block_3 %>%
  group_by(id, phase) %>%
  # Filter for the last 10 training trials and first 10 test trials
  filter(
    (phase == "training" & trial > max(trial) - n_training) |
    (phase == "test" & trial <= n_test)
  ) %>%
  group_by(id, phase, trial) %>%
  # Keep only the last row of each trial
  slice_tail(n = 1) %>%
  ungroup() %>%
  group_by(id, phase) %>%
  summarise(
    mean_distance = mean(distance, na.rm = TRUE),
    sd_distance = sd(distance, na.rm = TRUE),
    .groups = "drop"
  )

summary_stats_block_3
```

Blocks 1 and 2

```{r}
summary_stats_block_12 <- train_b12_test_b12 %>%
  group_by(id, phase, block) %>%
  # Filter for the last 10 training trials and first 10 test trials
  filter(
    (phase == "training" & trial > max(trial) - n_training) |
    (phase == "test" & trial <= n_test)
  ) %>%
  group_by(id, phase, trial, block) %>%
  # Keep only the last row of each trial
  slice_tail(n = 1) %>%
  ungroup() %>%
  group_by(id, phase, block) %>%
  summarise(
    mean_distance = mean(distance, na.rm = TRUE),
    sd_distance = sd(distance, na.rm = TRUE),
    .groups = "drop"
  )

summary_stats_block_12

```

### Increasing?

```{r}
#How many are increasing in means between training and test
wide_means <- summary_stats_block_12 %>%
  select(id, phase, mean_dist_mm) %>%
  pivot_wider(
    names_from = phase,
    values_from = mean_dist_mm
  )

num_increased <- wide_means %>%
  filter(test > training) %>%
  nrow()

total_participants <- nrow(wide_means)

cat("Participants with an increase:", num_increased,
    "out of", total_participants, "\n")
```

### Phase means

```{r}
#Blocks 1&2
phase_means <- summary_stats_block_12 %>%
  group_by(phase, block) %>%
  summarise(
    grand_mean = mean(mean_distance, na.rm = TRUE),
    grand_sd   = sd(mean_distance, na.rm = TRUE),
    n = n(),
    se = grand_sd / sqrt(n),
    .groups = "drop"
  )

phase_means

#Block 3
phase_means_overall <- summary_stats_block_3 %>%
  group_by(phase) %>%
  summarise(
    grand_mean = mean(mean_distance, na.rm = TRUE),
    grand_sd   = sd(mean_distance, na.rm = TRUE),
    n = n(),
    se = grand_sd / sqrt(n),
    .groups = "drop"
  )

phase_means_overall
```

## Linear Mixed Model

Blocks 1&2 interaction between training and test

```{r}
#blocks 1&2
m_simple <- lmer(
  distance ~ phase + (1 + phase | id),
  data = train_test_b12
)
summary(m_simple)
```

Block 1

```{r}
m_b1 <- lmer(
  distance ~ phase + (1 + phase | id),
  data = train_test_b1
)
summary(m_b1)
```

Block 2

```{r}
m_b2 <- lmer(
  distance ~ phase + (1 + phase | id),
  data = train_test_b2
)
summary(m_b2)
```

Test x block interaction: blocks 1 and 2

```{r}
m_block <- lmer(
  distance ~ phase * block + (1 + phase | id),
  data = train_test_b12
)
summary(m_block)
```

Test phase of groups 1 nd 2

```{r}
emmeans(m_block, ~ block | phase, at = list(phase = "test"))

lmer(distance ~ block + (1 | id), data = subset(train_test_b12, phase == "test"))
pairs(emmeans(m_block, ~ block | phase))

```

Block 3

```{r}
m_b3 <- lmer(
  distance ~ phase + (1 + phase | id),
  data = train_test_b3
)
summary(m_b3)
```

Blocks 1 & 3

```{r}
m_b13 <- lmer(
  distance ~ phase * block + (1 | id),
  data = train_test_b13
)

summary(m_b13)
```

```{r}
pairs(emmeans(m_b13, ~ block | phase))
```

```{r}
plot(m_simple, which = 1)

plot(m_simple, which = 2)

boxplot(distance ~ phase,   data = train_test_b12)

(colour_plot <- ggplot(train_test_b12, aes(x = trial, y = distance, colour = id)) +
  geom_point(size = 2) +
  theme_classic() +
  theme(legend.position = "none"))

#Note that trials 1-10 are test and trials 21-30 are training -> not in the correct order
(split_plot <- ggplot(aes(trial, distance), data = train_test_b12) + 
  geom_point() + 
  facet_wrap(~ id) + # create a facet for each mountain range
  xlab("trial") + 
  ylab("distance"))


```

## Speed and accuracy

Mean and SD for each participant

```{r}
speed_summary <- speed_ind %>%
  group_by(id, phase) %>%
  summarise(
    mean_speed = mean(speed_mm_s, na.rm = TRUE),
    SD_speed = sd(speed_mm_s, na.rm = TRUE),
    
    mean_dist_goal  = mean(distance_goal, na.rm = TRUE),
    
    .groups = "drop"
  )


speed_summary

```

Speed for groups 1 and 2

```{r}
speed_summary_b12 <- speed_ind %>%
  filter(block == 1 | block == 2) %>%
  group_by(id, phase, block) %>%
  summarise(
    mean_speed = mean(speed_mm_s, na.rm = TRUE),
    SD_speed = sd(speed_mm_s, na.rm = TRUE),
    
    mean_dist_goal  = mean(distance_goal, na.rm = TRUE),
    
    .groups = "drop"
  )
speed_summary_b12
```

Speed for group 1

```{r}
speed_summary_b1 <- speed_ind %>%
  filter(block == 1) %>%
  group_by(id, phase) %>%
  summarise(
    mean_speed = mean(speed_mm_s, na.rm = TRUE),
    SD_speed = sd(speed_mm_s, na.rm = TRUE),
    
    mean_dist_goal  = mean(distance_goal, na.rm = TRUE),
    
    .groups = "drop"
  )

speed_summary_b1

# Reshape to wide format: one row per participant, separate columns for training & test
speed_summary_b1_wide <- speed_summary_b1 %>%
  tidyr::pivot_wider(
    names_from = phase,
    values_from = c(mean_speed, SD_speed, mean_dist_goal),
    names_sep = "_"
  )

# Rank participants based on test phase performance (lowest distance = best) and add difference between training and test
speed_summary_b1_ranked <- speed_summary_b1_wide %>%
  arrange(mean_dist_goal_test) %>%
  mutate(
    diff_speed = mean_speed_training - mean_speed_test,
    rank_test = row_number()
    )

speed_summary_b1_ranked

```

Speed for group 2

```{r}
speed_summary_b2 <- speed_ind %>%
  filter(block == 2) %>%
  group_by(id, phase) %>%
  summarise(
    mean_speed = mean(speed_mm_s, na.rm = TRUE),
    SD_speed = sd(speed_mm_s, na.rm = TRUE),
    
    mean_dist_goal  = mean(distance_goal, na.rm = TRUE),
    
    .groups = "drop"
  )

speed_summary_b2



# Reshape to wide format: one row per participant, separate columns for training & test
speed_summary_b2_wide <- speed_summary_b2 %>%
  tidyr::pivot_wider(
    names_from = phase,
    values_from = c(mean_speed, SD_speed, mean_dist_goal),
    names_sep = "_"
  )



# Rank participants based on test phase performance (lowest distance = best) and add difference between training and test
speed_summary_b2_ranked <- speed_summary_b2_wide %>%
  arrange(mean_dist_goal_test) %>%
  mutate(
    diff_speed = mean_speed_training - mean_speed_test,
    rank_test = row_number()
    )

speed_summary_b2_ranked



```

```{r}
# Filter for test phase only
speed_test <- speed_ind %>%
  filter(phase == "test",
         block == 1)

# Plot: speed per trial
ggplot(speed_test, aes(x = trial, y = speed_mm_s, color = as.factor(id))) +
  geom_point(size = 2) +             # points for each trial
  geom_line(aes(group = id), alpha = 0.5) +  # optional: connect trials for each participant
  scale_x_continuous(breaks = sort(unique(speed_test$trial))) +
  labs(
    title = "Group 1: Speed in Trial During Test Phase",
    x = "Trial",
    y = "Speed (mm/s)",
    color = "Participant"
  ) +
  theme_minimal() +
  theme(legend.position = "right")
```

```{r}
speed_accuracy 
```

LLM

```{r}
speed_ind_b12 <- speed_ind %>%
  mutate(
    phase = factor(phase, levels = c("training", "test"))
  ) %>%
  filter(block %in% c(1, 2))

m_speed_12 <- lmer(
  speed_mm_s ~ phase * distance_goal + (1 + phase | id),
  data = speed_ind_b12
)
summary(m_speed_12)


correlation <- cor(speed_summary_b12$mean_dist_goal, speed_summary_b12$mean_speed, method = 'pearson')
correlation

partR2(
  m_speed_12,
  partvars = "phase:distance_goal",
  data = model.frame(m_speed_12),
  nboot = 1000
)
```

```{r}
m_speed_1 <- lmer(
  speed_mm_s ~ phase * distance_goal + (1 + phase | id),
  data = speed_ind_b1
)
summary(m_speed_1)
```

```{r}
speed_ind_b1 <- speed_ind %>%
  mutate(
    phase = factor(phase, levels = c("training", "test"))
  ) %>%
  filter(block == 1)


```

```{r}
m_speed_1 <- lmer(
  speed_mm_s ~ phase * distance_goal + (1 + phase | id),
  data = speed_ind_b1
)
summary(m_speed_1)

```

```{r}
m_speed_test_only <- lmer(
  speed_mm_s ~ distance_goal + (1 | id),
  data = speed_ind_b2 %>% filter(phase == "test")
)

summary(m_speed_test_only)
```

Block 2

```{r}
speed_ind_b2 <- speed_ind %>%
  mutate(
    phase = factor(phase, levels = c("training", "test"))
  ) %>%
  filter(block == 2)
```

```{r}
m_speed_2 <- lmer(
  speed_mm_s ~ phase * distance_goal + (1 + phase | id),
  data = speed_ind_b2
)
summary(m_speed_2)

```

PLOT

plot in speed from training to test in blocks 1 and a separate for block 2

(also a scatter plot distance to goal vs mean speed in testing)

```{r}
ggplot(speed_summary_b1,
       aes(x = phase,
           y = mean_speed,
           group = id,
           color = id)) +

  # ---- PARTICIPANT LINES ----
  geom_line(aes(color = id), alpha = 0.7, linewidth = 0.7) +
  geom_point(aes(color = id), size = 2, alpha = 0.5) +


  # ---- PARTICIPANT ERROR BARS ----
  geom_errorbar(
    aes(ymin = mean_speed - SD_speed,
        ymax = mean_speed + SD_speed),
    width = 0.06,
    alpha = 0.25
  ) +


  # ---- CLEANER LABELS ----
  labs(
    subtitle = "Group 1: Individual Accuracy in Training and Test Phases",
    x = "",
    y = "Speed (mm/s)",
    color = "Participant"
  ) +
  
  scale_x_discrete(labels = c(
    "training" = "Training",
    "test" = "Test"
  )) +

  # ---- IMPROVED THEME ----
  theme_minimal(base_size = 15) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    axis.text.x = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5)
  ) 

ggsave(
  "speed_g1_plot.png",
  width = 7,
  height = 5,
  dpi = 300,
  device = ragg::agg_png
)
```

```{r}
ggplot(speed_summary_b2,
       aes(x = phase,
           y = mean_speed,
           group = id,
           color = id)) +

  # ---- PARTICIPANT LINES ----
  geom_line(aes(color = id), alpha = 0.7, linewidth = 0.7) +
  geom_point(aes(color = id), size = 2, alpha = 0.5) +


  # ---- PARTICIPANT ERROR BARS ----
  geom_errorbar(
    aes(ymin = mean_speed - SD_speed,
        ymax = mean_speed + SD_speed),
    width = 0.06,
    alpha = 0.25
  ) +


  # ---- CLEANER LABELS ----
  labs(
    subtitle = "Group 2: Speed in Training and test phase",
    x = "",
    y = "Speed (mm/s)",
    color = "Participant"
  ) +
  
  scale_x_discrete(labels = c(
    "training" = "Training",
    "test" = "Test"
  )) +

  # ---- IMPROVED THEME ----
  theme_minimal(base_size = 15) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    axis.text.x = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5)
  ) 

ggsave(
  "speed_g2_plot.png",
  width = 7,
  height = 5,
  dpi = 300,
  device = ragg::agg_png
)
```

```{r}
speed_overall_b12 <- speed_summary_b12 %>%
  group_by(phase) %>%
  summarise(
    overall_mean_mm = mean(mean_speed, na.rm = TRUE),
    overall_sd_mm   = sd(mean_speed, na.rm = TRUE),
    .groups = "drop"
  )


ggplot(speed_summary_b12,
       aes(x = phase,
           y = mean_speed,
           group = id,
           color = id)) +

  # ---- PARTICIPANT LINES ----
  geom_line(aes(color = id), alpha = 0.7, linewidth = 0.7) +
  geom_point(aes(color = id), size = 2, alpha = 0.5) +


  # ---- PARTICIPANT ERROR BARS ----
  geom_errorbar(
    aes(ymin = mean_speed - SD_speed,
        ymax = mean_speed + SD_speed),
    width = 0.06,
    alpha = 0.25
  ) +
  
  # ---- OVERALL MEANS ----
  geom_line(
    data = speed_overall_b12,
    aes(x = phase, y = overall_mean_mm, group = 1),
    color = "black",
    linewidth = 0.8
  ) + 
  geom_point(
    data = speed_overall_b12,
    aes(x = phase, y = overall_mean_mm, group = 1),
    color = "black",
    size = 2.5,
    shape = 21,
    fill = "white",
    stroke = 1.0
  ) +
  geom_errorbar(
    data = speed_overall_b12,
    aes(
      x = phase,
      ymin = overall_mean_mm - overall_sd_mm,
      ymax = overall_mean_mm + overall_sd_mm,
      group = 1
    ),
    color = "black",
    width = 0.1,
    linewidth = 0.62
  ) + 


  # ---- CLEANER LABELS ----
  labs(
    subtitle = "Groups 1 and 2: Speed in training and test phase",
    x = "",
    y = "Speed (mm/s)",
    color = "Participant"
  ) +
  
  scale_x_discrete(labels = c(
    "training" = "Training",
    "test" = "Test"
  )) +

  # ---- IMPROVED THEME ----
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    axis.text.x = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5)
  )

ggsave(
  "speed_g12_plot.png",
  width = 7,
  height = 5,
  dpi = 300,
  device = ragg::agg_png
)
```

```{r}
# ---- OVERALL SUMMARY ----
speed_overall_b12 <- speed_summary_b12 %>%
  group_by(phase) %>%
  summarise(
    overall_mean_mm = mean(mean_speed, na.rm = TRUE),
    overall_sd_mm   = sd(mean_speed, na.rm = TRUE),
    .groups = "drop"
  )

# ---- PLOT ----
ggplot() +

  # ---- PARTICIPANT LINES ----
  geom_line(
    data = speed_summary_b12,
    aes(
      x = phase,
      y = mean_speed,
      group = id,
      color = id
    ),
    alpha = 0.7,
    linewidth = 0.7
  ) +

  geom_point(
    data = speed_summary_b12,
    aes(
      x = phase,
      y = mean_speed,
      color = id
    ),
    size = 2,
    alpha = 0.5
  ) +

  # ---- PARTICIPANT ERROR BARS ----
  geom_errorbar(
    data = speed_summary_b12,
    aes(
      x = phase,
      ymin = mean_speed - SD_speed,
      ymax = mean_speed + SD_speed,
      group = id
    ),
    width = 0.06,
    alpha = 0.25
  ) +

  # ---- OVERALL MEAN (BLACK + LEGEND ENTRY) ----
  geom_line(
    data = speed_overall_b12,
    aes(
      x = phase,
      y = overall_mean_mm,
      color = "Overall mean",
      group = 1
    ),
    linewidth = 0.9
  ) +

  geom_point(
    data = speed_overall_b12,
    aes(
      x = phase,
      y = overall_mean_mm,
      color = "Overall mean"
    ),
    size = 2.8,
    shape = 21,
    fill = "white",
    stroke = 1.0
  ) +

  geom_errorbar(
    data = speed_overall_b12,
    aes(
      x = phase,
      ymin = overall_mean_mm - overall_sd_mm,
      ymax = overall_mean_mm + overall_sd_mm,
      color = "Overall mean"
    ),
    width = 0.1,
    linewidth = 0.6
  ) +

  # ---- COLOR SCALE & LEGEND ----
  scale_color_manual(
    name = "Indicator",
    values = c("Overall mean" = "black"),
    guide = guide_legend(
      override.aes = list(alpha = 1)
    )
  ) +

  # ---- LABELS ----
  labs(
    subtitle = "Groups 1 and 2: Speed in training and test phase",
    x = "",
    y = "Speed (mm/s)"
  ) +

  scale_x_discrete(
    labels = c(
      "training" = "Training",
      "test" = "Test"
    )
  ) +

  # ---- THEME ----
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 9),
    legend.key.size = unit(0.6, "lines"),
    axis.text.x = element_text(size = 14, face = "bold")
  )
ggsave(
  "speed_g12_plot.png",
  width = 7,
  height = 5,
  dpi = 300,
  device = ragg::agg_png
)
```

```{r}
speed_summary_b12 %>%
  filter(phase == "test") %>%
  ggplot(aes(
    x = mean_dist_goal,
    y = mean_speed
  )) +
  geom_point(size = 2) +
  labs(
    x = "Mean Distance to Goal (mm)",
    y = "Mean Speed (mm/s)",
    colour = "Group",
    title = "Mean Speed vs Mean Distance to Goal (Test Phase)"
  ) +
  theme_minimal()

ggsave(
  "speed_dist_correlation_plot.png",
  width = 7,
  height = 5,
  dpi = 300,
  device = ragg::agg_png
)
```

compare top halve and bottom half

top fuve over colour, bottom 5 other colour

Moment by moment:

```{r}
ggplot(speed_last5cm_path,
       aes(x = path_mm, y = speed_mm_s, group = trial)) +
  geom_line(alpha = 0.2) +
  labs(
    x = "Distance Travelled in Final 5 cm (mm)",
    y = "Instantaneous Speed (mm/s)"
  ) +
  facet_wrap(~ phase)

one_subj <- speed_last5cm_path %>%
  filter(
    id == "004",
    phase == "test"
  )

ggplot(one_subj, aes(x = path_mm, y = speed_mm_s)) +
  
  # Individual trials (thin, transparent)
  geom_line(
    aes(group = trial),
    alpha = 0.3,
    colour = "grey40"
  ) +
  
  # Mean speed profile across trials
  stat_summary(
    aes(group = 1),
    fun = mean,
    geom = "line",
    linewidth = 1.2,
    colour = "blue"
  ) +
  
  labs(
    title = "Moment-by-Moment Speed in Final 5 cm",
    subtitle = "Participant 001 – First 10 Training Trials",
    x = "Distance Travelled in Final 5 cm (mm)",
    y = "Instantaneous Speed (mm/s)"
  ) +
  
  theme_minimal()

```

```{r}
ggplot(
  speed_last5cm_path %>% filter(id == "001"),
  aes(x = path_mm, y = speed_mm_s, colour = phase)
) +
  stat_summary(fun = mean, geom = "line", linewidth = 1.2) +
  scale_x_reverse() +
  theme_minimal()

```

```{r}
ggplot(
  speed_last5cm_path %>% filter(phase == "test", id != "007"),
  aes(x = path_mm, y = speed_mm_s)
) +
  
  # Individual trials
  geom_line(
    aes(group = trial),
    alpha = 0.3,
    colour = "grey40"
  ) +
  
  # Mean per participant
  stat_summary(
    aes(group = 1),
    fun = mean,
    geom = "line",
    linewidth = 0.8,
    colour = "blue"
  ) +
  
  facet_wrap(~ id) +
  
  labs(
    title = "Moment-by-Moment Speed in Final 5 cm",
    subtitle = "First 10 Test Trials – One Panel per Participant",
    x = "Distance Travelled in Final 5 cm (mm)",
    y = "Instantaneous Speed (mm/s)"
  ) +
  
  theme_minimal()

ggsave(
  "speed_final5cm_plot.png",
  width = 7,
  height = 5,
  dpi = 300,
  device = ragg::agg_png
)
```

```{r}
ggplot(
  speed_last5cm_path %>% filter(phase == "training", id != "007"),
  aes(x = path_mm, y = speed_mm_s)
) +
  
  # Individual trials
  geom_line(
    aes(group = trial),
    alpha = 0.3,
    colour = "grey40"
  ) +
  
  # Mean per participant
  stat_summary(
    aes(group = 1),
    fun = mean,
    geom = "line",
    linewidth = 0.8,
    colour = "blue"
  ) +
  
  facet_wrap(~ id) +
  
  labs(
    title = "Moment-by-Moment Speed in Final 5 cm",
    subtitle = "First 10 Test Trials – One Panel per Participant",
    x = "Distance Travelled in Final 5 cm (mm)",
    y = "Instantaneous Speed (mm/s)"
  ) +
  
  theme_minimal()

ggsave(
  "speed_final5cm_plot.png",
  width = 7,
  height = 5,
  dpi = 300,
  device = ragg::agg_png
)
```

## Self-report

```{r}
reliance_b12 <- train_test_b12 %>%
  distinct(id, reliance) %>%     # one row per participant
  count(reliance)

reliance_b12
```

```{r}
reliance_b1 <- train_test_b1 %>%
  distinct(id, reliance) %>%     # one row per participant
  count(reliance)

reliance_b1

congruent_re_b1 <- train_test_b1 %>%
  filter(reliance == "A")

congruent_re_b2 <- train_test_b2 %>%
  filter(reliance == "P")

congruent_reliance <- rbind(congruent_re_b1, congruent_re_b2)

congruent_reliance <- congruent_reliance %>%
  mutate(reliance_con = "con")

incongruent_re_b1 <- train_test_b1 %>%
  filter(reliance == "P")
incongruent_re_b2 <- train_test_b2 %>%
  filter(reliance %in% c("A", "A, P"))

incongruent_reliance <- rbind(incongruent_re_b1, incongruent_re_b2)
incongruent_reliance <- incongruent_reliance %>%
  mutate(reliance_con = "incon")

con_incon_groups12 <- rbind(congruent_reliance, incongruent_reliance) %>%
  mutate(
    phase = factor(phase, levels = c("training", "test")),
    reliance_con = factor(reliance_con, levels = c("incon", "con"))
  )


lmm_reliance <- lmer(
  distance ~ phase * reliance_con + (1 + phase | id),
  data = con_incon_groups12
)
summary(lmm_reliance)

####### Using this one 
lmm_reliance_v2 <- lmer(
  distance ~ phase * reliance_con + (1 | id), 
  data = con_incon_groups12
  )

summary(lmm_reliance_v2)

library(emmeans)
library(effectsize)

emm_phase <- emmeans(lmm_reliance_v2, ~ phase)

eff_size(
  emm_phase,
  sigma = sigma(lmm_reliance_v2),
  edf = df.residual(lmm_reliance_v2)
)


cohens_d(lmm_reliance_v2)

emm <- emmeans(lmm_reliance, ~ phase | reliance_con)

contrast(emm, method = "revpairwise")

```

```{r}
emm <- emmeans(lmm_reliance_v2, ~ phase | reliance_con)

plot(emm, comparisons = TRUE) + 
  labs(y = "Estimated distance")
```

Box plot:

```{r}
# Calculate mean and standard error for each phase and condition
summary_con_incon <- con_incon_groups12 %>%
  group_by(phase, reliance_con) %>%
  summarise(
    mean_distance_mm = mean(distance, na.rm = TRUE)/2.108,
    se_distance_mm = sd(distance, na.rm = TRUE) / sqrt(n()) /2.108
  )

# Create boxplot with error bars
ggplot(summary_con_incon, aes(x = reliance_con, y = mean_distance_mm, fill = phase)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  geom_errorbar(aes(ymin = mean_distance_mm - se_distance_mm, ymax = mean_distance_mm + se_distance_mm), width = 0.2, position = position_dodge(width = 0.8)) +
  labs(x = "Reliance", y = "Average Distance (mm)", fill = "Phase") +
  theme_minimal()

ggsave(
  "boxplot_reliance.png",
  width = 7,
  height = 5,
  dpi = 300,
  device = ragg::agg_png
)
```

Box plot version 2:

```{r}


ggplot(summary_con_incon, aes(x = reliance_con, y = mean_distance_mm, fill = phase)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  geom_errorbar(
    aes(ymin = mean_distance_mm - se_distance_mm, 
        ymax = mean_distance_mm + se_distance_mm), 
    width = 0.2, 
    position = position_dodge(width = 0.8)
  ) +
  # 1. Custom Labels for X-axis
  scale_x_discrete(labels = c("con" = "Congruent", "incon" = "Incongruent")) +
  
  # 2. Custom Colors and Legend Labels
  scale_fill_manual(
    values = c("training" = "lightgrey", "test" = "darkgrey"), 
    labels = c("Training", "Test")
  ) +
  
  # 3. Significance Interaction Indicator
  # Adjust 'y' to be just above your highest error bar in the Congruent group
  annotate("segment", x = 0.8, xend = 1.2, y = 50, yend = 50, colour = "black", linewidth = 0.6) +
  annotate("segment", x = 0.8, xend = 0.8, y = 49.5, yend = 50, colour = "black") +
  annotate("segment", x = 1.2, xend = 1.2, y = 49.5, yend = 50, colour = "black") +
  annotate("text", x = 1, y = 50.5, label = "*", size = 8) +
  
  labs(x = "Reliance", y = "Mean Distance to Goal (mm)", fill = "Phase", title = "Mean distance in training and test phases with self-reported reliance") +
  theme_minimal()

ggsave(
  "boxplot_reliance.png",
  width = 7,
  height = 5,
  dpi = 300,
  device = ragg::agg_png
)
```

```{r}
block1_A_ids <- train_test_b12 %>%
  filter(block == 1) %>%                 # tested on A only
  distinct(id, reliance) %>%
  filter(reliance == "A") %>%
  pull(id)

acc_train_test <- train_test_b12 %>%
  filter(id %in% block1_A_ids) %>%
  group_by(id, phase) %>%
  summarise(mean_acc = mean(distance, na.rm = TRUE),
            .groups = "drop") %>%
  tidyr::pivot_wider(
    names_from = phase,
    values_from = mean_acc
  ) %>%
  mutate(delta_acc = training - test)

acc_train_test %>%
  mutate(direction = ifelse(delta_acc > 0, "Increase in accuracy", "Decrease in accuracy")) %>%
  count(direction)
```

```{r}
ggplot(acc_train_test, aes(x = "", y = delta_acc)) +
  geom_boxplot() +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(
    x = "Block 1 – A-reliant participants",
    y = "Accuracy change (Test − Training)"
  )
```

```{r}
block2_P_ids <- train_test_b12 %>%
  filter(block == 2) %>%                 # tested on A only
  distinct(id, reliance) %>%
  filter(reliance == "P", reliance == "A,P") %>%
  pull(id)

acc_train_test_b2 <- train_test_b12 %>%
  filter(id %in% block2_P_ids) %>%
  group_by(id, phase) %>%
  summarise(mean_acc = mean(distance, na.rm = TRUE),
            .groups = "drop") %>%
  tidyr::pivot_wider(
    names_from = phase,
    values_from = mean_acc
  ) %>%
  mutate(delta_acc = training - test)

acc_train_test_b2 %>%
  mutate(direction = ifelse(delta_acc > 0, "Increase in accuracy", "Decrease in accuracy")) %>%
  count(direction)
```

Self report x chosen reliance x speed diff

```{r}

```

```{r}
lmm_reliance_speed <- lmer(
  speed_mm_s ~ phase * reliance_con + (1 | id), 
  data = con_incon_groups12
  )

summary(lmm_reliance_v2)
```

## Plots

Average distance to goal

```{r}
max_training <- 30
max_test <- 15

ggplot(summary_smoothed,
       aes(x = global_trial, y = mean_dist_smooth, color = phase, fill = phase)) +
  
  geom_line(size = 1) +
  
  geom_ribbon(aes(ymin = mean_dist_smooth - sd_dist_smooth,
                ymax = mean_dist_smooth + sd_dist_smooth),
            alpha = 0.2, color = NA) +
  
  geom_vline(xintercept = max_training + 0.5,
             linetype = "dotted", size = 1) +
  
  scale_x_continuous(
    breaks = c(seq(5, max_training, by = 5), max_training + seq(5, max_test, by = 5)),
    labels = c(seq(5, max_training, by = 5), seq(5, max_test, by = 5))
  ) +
  
  labs(
    title = "Distance to Goal Across Training and Test Trials",
    x = "Trial Number (Training 1–30, Test 1–15)",
    y = "Mean Distance to Goal ± SD (mm)"
  ) +
  
  theme_minimal(base_size = 14)

ggsave(
  "fig2_dist_goal.png",
  width = 7,
  height = 5,
  dpi = 300,
  device = ragg::agg_png
)
```

Individual means:

```{r}
ggplot(summary_stats_block_12,
       aes(x = phase,
           y = mean_dist_mm,
           group = id,
           color = as.factor(block))) +

  # ---- PARTICIPANT LINES ----
  geom_line(aes(color = as.factor(block)), alpha = 0.25, linewidth = 0.7) +
  geom_point(aes(color = as.factor(block)), size = 2, alpha = 0.5) +


  # ---- PARTICIPANT ERROR BARS ----
  geom_errorbar(
    aes(ymin = mean_dist_mm - sd_dist_mm,
        ymax = mean_dist_mm + sd_dist_mm),
    width = 0.06,
    alpha = 0.25
  ) +

  # ---- OVERALL MEANS ----
  geom_line(
    data = overall_summary,
    aes(x = phase, y = overall_mean_mm, color = "Overall Mean", group = 1),
    inherit.aes = FALSE,
    linewidth = 0.8
  ) +
  geom_point(
    data = overall_summary,
    aes(x = phase, y = overall_mean_mm, color = "Overall Mean", group = 1),
    inherit.aes = FALSE,
    size = 2.5,
    shape = 21,
    fill = "white",
    stroke = 1.0
  ) +
  geom_errorbar(
    data = overall_summary,
    aes(
      x = phase,
      ymin = overall_mean_mm - overall_sd_mm,
      ymax = overall_mean_mm + overall_sd_mm,
      color = "Overall Mean",
      group = 1
    ),
    inherit.aes = FALSE,
    width = 0.1,
    linewidth = 0.62
  ) +

  
  # ---- COLOR SCALE WITH NEW LEGEND ENTRY ----
  scale_color_manual(
    name = "Indicator",
    values = c(
      "1" = "#D55E00",
      "2" = "#0072B2",
      "Overall Mean" = "black"
    ),
    labels = c(
      "1" = "Group 1",
      "2" = "Group 2",
      "Overall Mean" = "Overall mean"
    )
  ) +

  # ---- CLEANER LABELS ----
  labs(
    subtitle = "Individual Accuracy in Training and Test Phases",
    x = "",
    y = "Mean Distance to Goal (mm)",
    color = "Block"
  ) +
  
  scale_x_discrete(labels = c(
    "training" = "Training",
    "test" = "Test"
  )) +

  # ---- IMPROVED THEME ----
  theme_minimal(base_size = 13) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    axis.text.x = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5)
  ) 

ggsave(
  "accuracy_plot.png",
  width = 7,
  height = 5,
  dpi = 300,
  device = ragg::agg_png
)
```

```{r}


ggplot(summary_stats_block_12,
       aes(x = phase,
           y = mean_dist_mm,
           group = id,
           color = as.factor(block))) +

  # ---- PARTICIPANT LINES ----
  geom_line(aes(color = as.factor(block)), alpha = 0.5, linewidth = 1) +
  geom_point(aes(color = as.factor(block)), size = 3, alpha = 0.6) +

  # ---- SMOOTHING ----
  geom_smooth(aes(color = as.factor(block)), method = "loess", se = FALSE, span = 0.2, linewidth = 1.5) +

  # ---- PARTICIPANT ERROR BARS ----
  geom_errorbar(
    aes(ymin = mean_dist_mm - sd_dist_mm,
        ymax = mean_dist_mm + sd_dist_mm),
    width = 0.06,
    alpha = 0.5
  ) +

  # ---- OVERALL MEANS ----
  geom_line(
    data = overall_summary,
    aes(x = phase, y = overall_mean_mm, color = "Overall Mean", group = 1),
    inherit.aes = FALSE,
    linewidth = 1.5
  ) +
  geom_point(
    data = overall_summary,
    aes(x = phase, y = overall_mean_mm, color = "Overall Mean", group = 1),
    inherit.aes = FALSE,
    size = 4,
    shape = 21,
    fill = "white",
    stroke = 1.5
  ) +
  geom_errorbar(
    data = overall_summary,
    aes(
      x = phase,
      ymin = overall_mean_mm - overall_sd_mm,
      ymax = overall_mean_mm + overall_sd_mm,
      color = "Overall Mean",
      group = 1
    ),
    inherit.aes = FALSE,
    width = 0.1,
    linewidth = 1
  ) +

  # ---- COLOR SCALE WITH NEW LEGEND ENTRY ----
  scale_color_manual(
    name = "Indicator",
    values = c(
      "1" = "#D55E00",
      "2" = "#0072B2",
      "Overall Mean" = "black"
    ),
    labels = c(
      "1" = "Block 1",
      "2" = "Block 2",
      "Overall Mean" = "Overall mean"
    )
  ) +

  # ---- CLEANER LABELS ----
  labs(
    subtitle = "Individual Accuracy in Training and Test Phases",
    x = "",
    y = "Mean Distance (mm)",
    color = "Block"
  ) +
  
  scale_x_discrete(labels = c(
    "training" = "Training",
    "test" = "Test"
  )) +

  # ---- IMPROVED THEME ----
  theme_minimal(base_size = 15) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    axis.text.x = element_text(size = 14, face = "bold"),
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5)
  )

```
